---
title: "Lenfest model indicators - calculation for EwE models"
author: "Linda Thomas, Camilla Novaglio, Beth Fulton & Javier Porobic"
date: "19/07/2021"
output: html_document
editor_options: 
chunk_output_type: console
---

# Indicator calculation for EwE models
This document provides the scripts to run the Priority 1 indicators for EwE models.
These are calculated using the model output files. Some additional information may be required to be collated.

# Clean up before you start
```{r}
rm(list=ls())
```

# load libraries
Below are the libraries to be loaded - first it runs the function that will check
# if the library is installed or not and if not then installs it so ready for usechecks if installed or not and if not then installs
```{r}
install_load <- function (this_package)  {
    package <- c(this_package)
    if(package %in% rownames(installed.packages()))
        do.call('library', list(package))
    ## if package is not installed locally, download, then load
    else {
        install.packages(package, dependencies=TRUE)
        do.call("library", list(package))
    }
}

### load/install libraries ###
# Data handling and table reshaping
install_load("tidyverse")
install_load("reshape2")
install_load("devtools")
install_load("MASS")
install_load("dplyr")
#install_load("Tool.R")
# Plotting
install_load("ggplot2")
install_load("RColorBrewer")
#install_load("ggbiplot")
install_load("plot3D")
install_load("plotly")
# PCA and Clustering
install_load("factoextra")
install_load("FactoMineR")
install_load("corrplot")
install_load("ape")
install_load("plot3D")
install_load("heatmaply")
install_load("data.table")
# Timeserise analysis
install_load("zoo")
#Other
install_load("Rcpp")
install_load("inline")
install_load("vegan")
install_load("patchwork")
install_load("cowplot")
install_load("ggpubr")
install_load("matrixStats")
install_load("drc")
install_load("viridis")
install_load("gridExtra")
install_load("cowplot")
#Network related
install_load("data.table")
install_load("magrittr")
install_load("qgraph")
install_load("visNetwork")
install_load("intergraph")
install_load("tidygraph")
#install_load("network")
install_load("igraph")
```

# Helpful fucntion for loading EwE files
```{r}
##' @title Skip line function. this automatically get the number of rows based on the ewe version
##' @param file EwE .csv output file
##' @return Number of lines to skip
##' @author Javier Porobic
skip_lines <- function(file){
    strs  <- readLines(file)
    lines <- grep('year\\\\group,', strs) -1
    return(lines)
}
```

# Data collection  
Please set the working directory to where the model output files are.  

Additional information to be provided by the modeller:  
* A list of species used in your model in csv format (e.g ID, Group). This can be taken from the model parameters file used to set up the model.  
* L inf for each species in the model. This is taken from the model parameter file. Calculate the mean L infinity for the species group.
* size categories for each species in csv format (e.g. species_id, Group, size). The information is taken from the model parameters file. Categorise each group into L, S or split depending on total length (small = <30cm, large = >50cm, SPLIT = 30-50cm).

```{r}

# Palettes to use
tscolor <- "red4"
aggtscolor <-"deepskyblue4"
aggtscolor2 <- "deepskyblue"
textsize <- 16
linesize <- 3
nPanel <- 12
use_weights <- 1
chl_from_file <- 0
bo_in_same_file <- 0
bo_conservative <- 1
bo_yr_row <- 0 # Set to 0 if you want the final row of the file
## Area of model in km2 (whole of SESSF = 3700000), EBS smaller
area_model <- 940000

# Define the relevant directories - all these paths (including the output directories) must already exist
mainDir <- "Set_main_directory_here_it_is_directory_above_the_EwE_output_folders"

OutsubDirStep1 <- "Output_of_analysis_folder"
BosubDir <- "Directory_name_for_no_fishing_case"

InputsubDir  <- "Folder_name_of_scenario_to_analyse"

OutsubDirStep2 <- "Where_you_want_to_save_analysis_outputs"

```

# Load the data
```{r}
# set working directory - change to where your model output files are.
setwd(mainDir)
OutsubDirStep3 <- paste(OutsubDirStep1,"/",OutsubDirStep2,sep="")
OutDir <- paste(mainDir,"/",OutsubDirStep3,sep="")
#skip_this  <- header_row_ID - 1

# Create output directory if required
ifelse(!dir.exists(file.path(mainDir, OutsubDirStep1)), dir.create(file.path(mainDir, OutsubDirStep1)), FALSE)
ifelse(!dir.exists(file.path(mainDir, OutsubDirStep3)), dir.create(file.path(mainDir, OutsubDirStep3)), FALSE)
if(!dir.exists(file.path(OutDir))) dir.create(file.path(OutDir))

# read in EwE data
# find model start year from an output file
BioFile <- paste(mainDir,"/",InputsubDir,"/","biomass_annual.csv",sep="")
d <- read.csv(BioFile, header = FALSE)
s_year = d[c(1:7), ];               # this reads the first 7 rows of the header to give the start year of the model.

# catch data
CatchFile <- paste(mainDir,"/",InputsubDir,"/","catch_annual.csv",sep="")
skip_this <- skip_lines(CatchFile)
catch <- read.csv(CatchFile, header = T, skip = skip_this, check.names = FALSE) # because csv file has headers - will need to skip the first 9 rows; check names makes sure an X isn't added before the number for the species
names(catch)[1] <- 'Year'   # changes the name of the first column to year instead of year//group

# aggregate landings data
LandFile <- paste(mainDir,"/",InputsubDir,"/","landings_annual.csv",sep="")
landings <- read.csv(LandFile, header = T, skip = skip_this, check.names = FALSE) # because csv file has headers - will need to skip the first 9 rows; check names makes sure an X isn't added before the number for the species
names(landings)[1] <- 'Year'   # changes the name of the first column to year instead of year//group
names(landings)[3] <- 'species_id'   # changes the name of the first column to year instead of year//group

# biomass data
biomass <- read.csv(BioFile, header = T, skip = skip_this, check.names = FALSE)
names(biomass)[1] <- 'Year'

# total catch and landings data per fleet
RemFile <- paste(mainDir,"/",InputsubDir,"/","catch-fleet-group_annual.csv",sep="")
removals_fleet <- read.csv(RemFile, header = T, skip = skip_this, check.names = FALSE)
names(removals_fleet)[1] <- 'Year'
LFFile <- paste(mainDir,"/",InputsubDir,"/","landings_annual.csv",sep="")
landings_fleet <- read.csv(LFFile, header = T, skip = skip_this, check.names = FALSE)
names(landings_fleet)[1] <- 'Year'

# species id - put names
id <- read.csv("Species_ID.csv") # You will need to put in the name of your species list csv file here
nSPName <- length(unique(id$Group))
SpeciesNames <- id$Group

# fleet id - put names
idf <- read.csv("Fleet_ID.csv") # You will need to put in the name of your species list csv file here
nFName <- length(unique(idf$FleetName))
FleetNames <- idf$FleetName

# mortality data
MortFile <- paste(mainDir,"/",InputsubDir,"/","mort-fleet-group_annual.csv",sep="")
mortality_fleet <- read.csv(MortFile, header = T, skip = skip_this, check.names = FALSE)
names(mortality_fleet)[1] <- 'Year'
MortFile <- paste(mainDir,"/",InputsubDir,"/","mortality_annual.csv",sep="")
mortality <- read.csv(MortFile, header = T, skip = skip_this, check.names = FALSE)
names(mortality)[1] <- 'Year'

# trophic level data
TLFile <- paste(mainDir,"/",InputsubDir,"/","tl_annual.csv",sep="")
tl_annual <- read.csv(TLFile, header = T, skip = skip_this, check.names = FALSE)
names(tl_annual)[1] <- 'Year'   # changes the name of the first column to year instead of year//group

# weight data
WeightFile <- paste(mainDir,"/",InputsubDir,"/","weight_annual.csv",sep="")
weight_annual <- read.csv(WeightFile, header = T, skip = skip_this, check.names = FALSE)
names(weight_annual)[1] <- 'Year'   # changes the name of the first column to year instead of year//group

# chl file if present
if (chl_from_file > 0) {
  ChlFile <- paste(mainDir,"/",InputsubDir,"/","chl.csv",sep="")   # Assumes a format of Year chl
  dfChl <- read.csv(ChlFile, header = T, check.names = FALSE)
  
  # make sure has columns Year and Chl
}

# convert data into a data frame and pivot tables to tidy
bio <- as.data.frame(biomass) %>% 
  pivot_longer(-Year, names_to = "species_id", values_to = "biomass_tonnes")
bio$biomass_tonnes <- area_model * bio$biomass_tonnes

cat <- as.data.frame(catch) %>% 
  pivot_longer(-Year, names_to = "species_id", values_to = "catch_tonnes")
cat$catch_tonnes <- area_model * cat$catch_tonnes

aggland <- landings %>%
  group_by(Year, species_id) %>%
  dplyr::summarise(landings_tonnes = sum(value))
aggland$landings_tonnes <- area_model * aggland$landings_tonnes
aggland$species_id <- as.character(aggland$species_id)

tl <- as.data.frame(tl_annual) %>% 
  pivot_longer(-Year, names_to = "species_id", values_to = "trophic_level")

land <- as.data.frame(landings_fleet) %>% 
  dplyr::rename(species_id = group) %>% # rename group to species_id
  dplyr::rename(fleet_landing_tonnes = value) %>% # rename value to landing_tonnes
  mutate(species_id = as.character(species_id)) %>% 
  unique()
land$fleet_landing_tonnes <- area_model * land$fleet_landing_tonnes

removals <- as.data.frame(removals_fleet) %>% 
  dplyr::rename(species_id = group) %>% # rename group to species_id
  dplyr::rename(fleet_removals_tonnes = value) %>% # rename value to landing_tonnes
  mutate(species_id = as.character(species_id)) %>% 
  unique()
removals$fleet_removals_tonnes <- area_model * removals$fleet_removals_tonnes

# add in species names to the data frame
## change the COL_ID to species_id so can join
id2 <- id %>% 
  dplyr::rename(species_id = ID) %>%  # specify that the dplyr rename is the function you want & rename ID to species_id
#    select(-COL_ID) %>% # removes the COL_ID column
  mutate(species_id = as.character(species_id)) %>% # change to character so same as other data frame
  unique() # make sure only unique values are used.

# merge the catch and biomass into one data frame
df1tmp <- full_join(bio, cat) # have two columns the same so they will automatically join on these
df1 <- full_join(df1tmp, aggland)
df1[is.na(df1)] <- 0
df <- full_join(df1, id2) # data frame with biomass, catch and species names

# df3 <- full_join(df, land) %>% # data frame with biomass, catch and species names & landings
#  select(Year, species_id, Group, fleet, biomass_tonnes, catch_tonnes, fleet_landing_tonnes) # reorder the columns so they are easier to read

# New df3 which has landings and total catch per fleet in one file
df3tmp <- full_join(land, removals)

# Join landings and species names
df3tmpA <- full_join(df3tmp, id2) 
df3 <- merge(df3tmpA, idf, by.x = "fleet", by.y = "ID") 

# add species names to trophic level data
tl_species <- full_join(tl, id2)

# Get reference values
# Depending on the value of bo_conservative set Bo
# bo_in_same_file = 1 then take Bs from row bo_yr_row
# bo_in_same_file = 0 and bo_conservative = 0 then take Bs from the Bo file as dicatted by bo_yr_row
# bo_in_same_file = 0 and bo_conservative = 1 then take max(first row of biofile, row of Bo file)

if(bo_in_same_file < 1){
  # Load Bo and Mo from files
  #bo_skip_this <- bo_header_row_ID - 1
  BoBioFile <- paste(mainDir,"/",BosubDir,"/","biomass_annual.csv",sep="")
  bo_skip_this <- skip_lines(BoBioFile)
  BoBio <- read.csv(BoBioFile, header = T, skip = bo_skip_this, check.names = FALSE)
  MoMortFile <- paste(mainDir,"/",BosubDir,"/","mortality_annual.csv",sep="")
  MoMort <- read.csv(MoMortFile, header = T, skip = bo_skip_this, check.names = FALSE)
  names(BoBio)[1] <- 'Year'
  names(MoMort)[1] <- 'Year' 
  if(bo_yr_row < 1) {
    bo_yr_row <- length(BoBio[,1])
    RefB <- BoBio[bo_yr_row,]
    RefM <- MoMort[bo_yr_row,]
    
  } else {
    RefB <- BoBio[bo_yr_row,]
    RefM <- MoMort[bo_yr_row,]
  }
  
  if(bo_conservative > 0) {
    altB1 <- as.data.frame(RefB) %>% 
      pivot_longer(-Year, names_to = "species_id", values_to = "RefB")
    altBtmp <- biomass[1,]
    altB2 <- as.data.frame(altBtmp) %>% 
      pivot_longer(-Year, names_to = "species_id", values_to = "RefB")
    altB1$Year <- RefM[1,1]
    altB2$Year <- RefM[1,1]
    dftmp <- merge(altB1, altB2, by=c("Year","species_id"))
    dftmp$RefB <- ifelse(dftmp$RefB.x > dftmp$RefB.y, dftmp$RefB.x, dftmp$RefB.y)
    dfRefB <- dftmp
    dfRefB <- subset (dfRefB, select = -c(Year, RefB.x, RefB.y))
  } else {
    dfRefB <- as.data.frame(RefB) %>% 
      pivot_longer(-Year, names_to = "species_id", values_to = "RefB")
    dfRefB <- subset (dfRefB, select = -c(Year))
  }
  dfRefM <- as.data.frame(RefM) %>% 
    pivot_longer(-Year, names_to = "species_id", values_to = "RefM")
  dfRefM <- subset (dfRefM, select = -c(Year))
  
} else {
  # Assumes has sensible reference year rown number
  RefB <- biomass[bo_yr_row,]
  RefM <- mortality[bo_yr_row,]
  
  dfRefB <- as.data.frame(RefB) %>% 
    pivot_longer(-Year, names_to = "species_id", values_to = "RefB")
  dfRefB <- subset (dfRefB, select = -c(Year))
  dfRefM <- as.data.frame(RefM) %>% 
    pivot_longer(-Year, names_to = "species_id", values_to = "RefM")
  dfRefM <- subset (dfRefM, select = -c(Year))

}
dfRef <- merge(dfRefM, dfRefB, by=c("species_id")) # Intentional reuse
dfRef$RefBo <- area_model * dfRef$RefB

```

# Greenband
Follows the approach of Heath - where the allowed catch is proportional to production
```{r}
# Set up reference values
RefVal <- dfRef
RefVal$RefP <- RefVal$RefB * RefVal$RefM
idRef <- merge(id2, RefVal, by=c("species_id"))
idRef <- idRef %>% dplyr::filter(IsDetritus < 1)

# Estimate the initial slope
idRef$logP <- log10(idRef$RefP)
idRef$logB <- log10(idRef$RefB)
linreg <- lm(formula = logB ~ logP, data = idRef)
matrix_coef <- summary(linreg)$coefficients 
reg_slope <- round(matrix_coef[2,1],3)
reg_const <- round(matrix_coef[1,1],3)
band_slope <- reg_slope + 1.0   # This is the slope of the grend band for the rest of the work
lm_equation <- paste("y = ", reg_const, " + ", reg_slope, " x",sep="")
this_r2 <- round(summary(linreg)$r.squared,3)
lm_R2 <- paste("R2 = ",this_r2,sep="")

ymin <- 1e-8
xmin <- 1e-6
ymax <- 1e+5
xmax <- 1e+5
lymin <- log10(1e-8)
lxmin <- log10(1e-6)
lymax <- log10(1e+5)
lxmax <- log10(1e+5)

outaplot <- paste(OutDir,"/Green_Band_Reference_Plot.png",sep="")
ggplot(data = idRef, aes(x = RefP, y = RefB)) + 
    geom_point() +
    geom_smooth(method='lm') +
    scale_x_log10(limits=c(xmin, xmax)) + scale_y_log10(limits=c(ymin, ymax)) +
    labs(x="Production", y = "Biomass") +
    annotate("text", x=1e-4, y=3e+4, label= lm_equation) + 
    annotate("text", x = 1e-4, y=1e+4, label = lm_R2) +
    theme(axis.text=element_text(size=16,face="bold"), axis.title=element_text(size=20,face="bold"))
ggsave(file=outaplot)

# Get production once fished
production <- mortality * biomass
production$Year <- biomass$Year
dfProd <- as.data.frame(production) %>% 
  pivot_longer(-Year, names_to = "species_id", values_to = "Production")
dftmp <- full_join(dfProd, id2) # Reuse old temporary df
dfBand <- full_join(dftmp, df) 
dfBand <- dfBand %>% dplyr::filter(Class_Code > 0)

# Rate in comparison to green band
# Equations for key lines
# Max_allowable  C = 0.5 * P
# Max_green_band  C = P ^ band_slope
# Min_green_band  C = C_Max_green_band * 0.01
# Realised Max_green_band  C = min(Max_allowable, Max_green_band)
# Realised Min_green_band  C = min(Max_allowable, Min_green_band)
# Light 1 - L
# Acceptable 2 - A
# Fail 3 - F
  
dfBand$MaxAllow <- 0.5 * dfBand$Production
dfBand$MaxGreenBand <- dfBand$Production ^ band_slope
dfBand$MinGreenBand <- dfBand$MaxGreenBand * 0.01
dfBand$RealMax <- ifelse(dfBand$MaxAllow < dfBand$MaxGreenBand, dfBand$MaxAllow , dfBand$MaxGreenBand)
dfBand$RealMin <- ifelse(dfBand$MaxAllow < dfBand$MinGreenBand, dfBand$MaxAllow , dfBand$MinGreenBand)
dfBand$catch <- dfBand$catch_tonnes / area_model
#dfBand$DistortScore <- ifelse(dfBand$catch_tonnes < dfBand$RealMin, "L", (ifelse(dfBand$catch_tonnes >= dfBand$RealMax, "F", "A")))
dfBand$DistortScore <- ifelse(dfBand$catch < dfBand$RealMin, "L", (ifelse(dfBand$catch >= dfBand$RealMax, "F", "A")))
  
dfScored <- merge(dfBand, dfRef, by=c("species_id"))
names(dfScored)[names(dfScored) == "species_id.x"] <- "species_id"
names(dfScored)[names(dfScored) == "Classification.x"] <- "Classification"
names(dfScored)[names(dfScored) == "Class_Code.x"] <- "Class_Code"

dfScored$Rel_B <- dfScored$biomass_tonnes / dfScored$RefBo
dfScored$Min_B <- ifelse(dfScored$Class_Code == 1, 0.5, 
                           (ifelse(dfScored$Class_Code == 2, 0.3, 
                                   (ifelse(dfScored$Class_Code == 3, 0.35, 
                                           (ifelse(dfScored$Class_Code == 4, 0.2, 
                                                   (ifelse(dfScored$Class_Code == 5, 0.4, 
                                                           (ifelse(dfScored$Class_Code == 6, 0.4, 0.6)))))))))))
dfScored$Max_B <- ifelse(dfScored$Class_Code == 1, 0.7, 
                           (ifelse(dfScored$Class_Code == 2, 0.6, 
                                   (ifelse(dfScored$Class_Code == 3, 0.4, 
                                           (ifelse(dfScored$Class_Code == 4, 0.4, 
                                                   (ifelse(dfScored$Class_Code == 5, 0.5, 
                                                           (ifelse(dfScored$Class_Code == 6, 0.5, 0.7)))))))))))
dfScored$B_Score <- ifelse(dfScored$Rel_B > dfScored$Max_B, "L", (ifelse(dfScored$Rel_B <= dfScored$Min_B, "F", "A")))
  
# Assumes Thresholds
# 
#  CLass    ID    Min   Max
#
# Vulnerable  1   0.5   0.7  
# Habitat     2   0.3   0.6
# Byproduct   3   0.35  0.4
# Bycatch     4   0.2   0.4
# Target      5   0.4   0.5
# Robust      6   0.4   0.5
# Hub         7   0.6   0.7
  
# Aggregate Results
dfAggScore_Distort <- dfScored %>% dplyr::count(Year, DistortScore)
dfAggScore_B <- dfScored %>% dplyr::count(Year, B_Score)
  
dfAggScore_Distort <- dfAggScore_Distort %>% dplyr::filter(!is.na(DistortScore))
dfAggScore_B <- dfAggScore_B %>% dplyr::filter(!is.na(B_Score))
  
# Plot Scores through time - as bar plot
outPlotName <- paste(OutDir,"/GreenBand-aggregate-score.png",sep="")
ggplot(data = dfAggScore_Distort, aes(x = Year, y = n, fill = DistortScore)) + geom_bar(colour = "black", stat="identity", size = 0.1) +
    scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) + theme_bw() +
    labs(x="Years", y = "Ratings") +
    theme(axis.text=element_text(size=16,face="bold"), axis.title=element_text(size=20,face="bold"))
ggsave(file=outPlotName) 

# Plot Scores through time - as bar plot
outPlotName <- paste(OutDir,"/GreenBand-aggregate-scoreB.png",sep="")
ggplot(data = dfAggScore_B, aes(x = Year, y = n, fill = B_Score)) + geom_bar(colour = "black", stat="identity", size = 0.1) +
    scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) + theme_bw() +
    labs(x="Years", y = "Ratings") +
    theme(axis.text=element_text(size=16,face="bold"), axis.title=element_text(size=20,face="bold"))
ggsave(file=outPlotName) 
 
Bounds <- data.frame(matrix(0, ncol = 6, nrow = 10))
colnames(Bounds)[1:6] <- c("P","MaxAllow","MaxGreenBand","MinGreenBand","MinC","MaxC")
listP <- c(1.00E-19, 0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)
Bounds$P <- listP
Bounds$MaxAllow <- 0.5 * Bounds$P
Bounds$MaxGreenBand <- Bounds$P ^ band_slope
Bounds$MinGreenBand <- Bounds$MaxGreenBand * 0.01
Bounds$MaxC <- ifelse(Bounds$MaxAllow < Bounds$MaxGreenBand, Bounds$MaxAllow, Bounds$MaxGreenBand)
Bounds$MinC <- ifelse(Bounds$MaxAllow < Bounds$MinGreenBand, Bounds$MaxAllow, Bounds$MinGreenBand)
BoundsMelt <- melt(Bounds,"P") 
names(BoundsMelt)[2] <- 'Variables'
names(BoundsMelt)[3] <- 'CValue'

# Per km2 results
nSpCode <- max(dfScored$Class_Code)
for (i in 1:nSpCode) {
  dfThisCode <- dfScored %>% dplyr::filter(Class_Code == i)
  outPlotName <- paste(OutDir,"/GreenBand-",dfThisCode$Classification[1],"_Per_Area.png",sep="")
  
  dfMin <- BoundsMelt %>% dplyr::filter(Variables == "MinC")
  dfMax <- BoundsMelt %>% dplyr::filter(Variables == "MaxC")

  #ymin <- min(dfThisCode$C) * 0.1
  #xmin <- min(dfThisCode$P) * 0.1
  #ymax <- max(dfThisCode$C) * 10.0
  #xmax <- max(dfThisCode$P) * 10.0
  
  ggplot(data = dfThisCode, aes(x = Production, y = catch)) + 
    geom_point(data = dfThisCode, aes(size = Year, color = Group)) +
    geom_line(data = dfThisCode, aes(color = Group)) +
    geom_line(data = dfMin, aes(x = P, y = CValue), linetype = "dashed", color = "black") +
    geom_line(data = dfMax, aes(x = P, y = CValue), linetype = "dashed", color = "black") +
    scale_size_continuous(range = c(1, 3)) +
    scale_x_log10(limits=c(xmin, xmax)) + scale_y_log10(limits=c(ymin, ymax)) +
    labs(x="Production", y = "Catch") +
    theme(axis.text=element_text(size=10,face="bold"), axis.title=element_text(size=20,face="bold"))
  
  ggsave(file=outPlotName)
  
}

## Total (so area corrected) results
ymin <- 1e-5 
xmin <- 1e-5
ymax <- 1e+10
xmax <- 1e+10

for (i in 1:nSpCode) {
  dfThisCode <- dfScored %>% dplyr::filter(Class_Code == i)
  outPlotName <- paste(OutDir,"/GreenBand-",dfThisCode$Classification[1],".png",sep="")
  
  dfThisCode$P<- dfThisCode$Production * area_model
  
  dfMin <- BoundsMelt %>% dplyr::filter(Variables == "MinC")
  dfMax <- BoundsMelt %>% dplyr::filter(Variables == "MaxC")
  
  dfMin$Pa <- dfMin$P * area_model
  dfMin$Ca <- dfMin$CValue * area_model
  dfMax$Pa <- dfMax$P * area_model
  dfMax$Ca <- dfMax$CValue * area_model
  
  write.csv(dfThisCode, file = "Target_Results.csv", row.names = FALSE)
  write.csv(dfMin, file = "Target_Min.csv", row.names = FALSE)
  write.csv(dfMax, file = "Target_Max.csv", row.names = FALSE)
  
  #ymin <- min(dfThisCode$C) * 0.1
  #xmin <- min(dfThisCode$P) * 0.1
  #ymax <- max(dfThisCode$C) * 10.0
  #xmax <- max(dfThisCode$P) * 10.0
  
  ggplot(data = dfThisCode, aes(x = P, y = catch_tonnes)) + 
    geom_point(data = dfThisCode, aes(size = Year, color = Group)) +
    geom_line(data = dfThisCode, aes(color = Group)) +
    geom_line(data = dfMin, aes(x = Pa, y = Ca), linetype = "dashed", color = "black") +
    geom_line(data = dfMax, aes(x = Pa, y = Ca), linetype = "dashed", color = "black") +
    scale_size_continuous(range = c(0.5, 2)) +
    scale_x_log10(limits=c(xmin, xmax)) + scale_y_log10(limits=c(ymin, ymax)) +
    labs(x="Production", y = "Catch") +
    guides(col = guide_legend(ncol = 3)) +
    theme(axis.text=element_text(size=10,face="bold"), axis.title=element_text(size=20,face="bold"))
  
  ggsave(file=outPlotName)
  
}
```
